An Analysis of Performance Bottlenecks in MRI Pre-Processing

### 2024-10-11 paper/paper.tex
Fix table and figures to improve clarity.

\csvnames{csvcol}{1=\pipeline, 2=\mem, 3=\la, 4=\lb, 5=\lc, 6=\dram, 7=\store, 8=\disk}
\csvstyle{memory_bound}{
	tabular = |r|c|c|c|c|c|c|c|,
	table head = \hline Pipeline &  \% Memory Bound &  \% L1 Bound &  \% L2 Bound &  \% L3 Bound & \% DRAM Bound & \% Store Bound & \% Disk Bound\\\hline\hline,
	late after line = \\\hline,
	respect all,
	csvcol
}
\begin{table*}[ht]
	\centering
	\csvreader[memory_bound]{tables/memory_bound.csv}{}
	{\pipeline & \tablenum[round-precision=2]{\mem} & \tablenum[round-precision=2]{\la} & \tablenum[round-precision=2]{\lb} & \tablenum[round-precision=2]{\lc} & \tablenum[round-precision=2]{\dram} & \tablenum[round-precision=2]{\store} & \tablenum[round-precision=2]{\disk}}
	\caption{Impact of data load on stalled CPU cycles. For each metric \HL{(Total, L1, L2, L3, DRAM, Store, and Disk Fetch)}, reported values are summations weighted by function CPU time, averaged over $n=20$ subjects, and collected in single-threaded mode. They represent the percentage of the total CPU time stalled for the metric.}
	\label{extab:memory-bound}
\end{table*}

@@

\begin{figure*}
	\centering
	\begin{subfigure}[t]{0.49\textwidth}
		\caption{Single-threaded}
		\label{subfig:hotspots-freesurfer-reconall-1thread}
		\includegraphics[width=\textwidth]{figures/hotspots-1threads-freesurfer-reconall-simple.png}
	\end{subfigure}
	\begin{subfigure}[t]{0.49\textwidth}
		\caption{Multi-threaded (32 threads)}
		\label{subfig:hotspots-freesurfer-reconall-32threads}
		\includegraphics[width=\textwidth]{figures/hotspots-32threads-freesurfer-reconall-simple.png}
	\end{subfigure}
	\caption{FreeSurfer recon-all analysis. The y-axis shows the average CPU time spent in each function, with error bars showing the standard deviation across n=20 subjects. The x-axis shows the function ordered by decreasing CPU time grouped by module. We only display module names and omitted function names for clarity.}
	\label{fig:hotspots-freesurfer-reconall}
\end{figure*}

>>>>

\csvnames{csvcol}{1=\pipeline, 2=\mem, 3=\la, 4=\lb, 5=\lc, 6=\dram, 7=\store, 8=\disk}
\csvstyle{memory_bound}{
	tabular = |r|c||c|c|c|c|c|c|,
	table head = \hline Pipeline &  Total Memory Bound \% & L1 \% & L2 \% &  L3 \% & DRAM \% & Store \% & Disk Fetch \%\\\hline\hline,
	late after line = \\\hline,
	respect all,
	csvcol
}
\begin{table*}[ht]
	\centering
	\csvreader[memory_bound]{tables/memory_bound.csv}{}
	{\pipeline & \tablenum[round-precision=2]{\mem} & \tablenum[round-precision=2]{\la} & \tablenum[round-precision=2]{\lb} & \tablenum[round-precision=2]{\lc} & \tablenum[round-precision=2]{\dram} & \tablenum[round-precision=2]{\store} & \tablenum[round-precision=2]{\disk}}
	\caption{Impact of data load on stalled CPU cycles. For each metric \HL{(Total, L1, L2, L3, DRAM, Store, and Disk Fetch)}, reported values are summations weighted by function CPU time, averaged over $n=20$ subjects, and collected in single-threaded mode. They represent the percentage of the total CPU time stalled for the metric.}
	\label{extab:memory-bound}
\end{table*}

@@

\begin{figure*}
	\centering
	\begin{subfigure}[t]{0.49\textwidth}
		\caption{Single-threaded}
		\label{subfig:hotspots-freesurfer-reconall-1thread}
		\includegraphics[width=\textwidth]{figures/hotspots-1threads-freesurfer-reconall-simple.png}
	\end{subfigure}
	\begin{subfigure}[t]{0.49\textwidth}
		\caption{Multi-threaded (32 threads)}
		\label{subfig:hotspots-freesurfer-reconall-32threads}
		\includegraphics[width=\textwidth]{figures/hotspots-32threads-freesurfer-reconall-simple.png}
	\end{subfigure}
	\caption{FreeSurfer recon-all analysis. Error bars show the standard deviation across n=20 subjects. The x-axis shows the function ordered by decreasing CPU time grouped by module. We only display module names and omitted function names for clarity.}
	\label{fig:hotspots-freesurfer-reconall}
\end{figure*}
